---
title: "APIscraping_part2"
author: "Asaf Eliyahu & Einat Edelstien"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(twitteR)
library(tm)
library(wordcloud)
library(stringr)
library(wordcloud)
library(plyr)
library(ggplot2)
source("sentiment.R")
consumerKey <- 'd9Ie2YnVqLCJQZInCe59iEd7G'
consumerSecret <- 'j7Hjsz4Lza7D8MyrlkpPiSAA9Vtxu0fp0bCBRZa186Hw0jyIBa'
accessToken <- '718353560489095168-YtKnMnbcpPnvWH6du6SDhdtS9ecbHg9'
accessTokenSecret <- 'REOHKpbejvg6si5jXNJDffEbCLrRc9i9oaOv3X5FpWRoL'
twitteR::setup_twitter_oauth(consumerKey,consumerSecret,accessToken,accessTokenSecret)
```

## NBA analysis markdown

In part2 we decided to use twitteR which is a tool that aloud us to search for specific twitts with specific words inside of them.
we decided to look for twitts which include the word #NBA in them.

####first we display a "wordCloud" of the most common words

```{r twitteR, echo=FALSE}

# get tweets with relevant data
NBAtweets <- searchTwitter('#NBA', n = 500, lang = 'en', resultType = "recent")

NBAtweets_text <- sapply(NBAtweets, function(x) x$getText())
# Now we can use tm package to make a corpus and then we can view it as a wordcloud
NBAtweets_corpus <- Corpus(VectorSource(NBAtweets_text))

#cleaning the data a bit
NBAtweets_corpus_clean <- tm_map(NBAtweets_corpus, removePunctuation)
NBAtweets_corpus_clean <- tm_map(NBAtweets_corpus_clean, removeWords, stopwords("english"))
NBAtweets_corpus_clean <- tm_map(NBAtweets_corpus_clean, removeNumbers)
NBAtweets_corpus_clean <- tm_map(NBAtweets_corpus_clean, stripWhitespace)

#making a wordcloud
wordcloud(NBAtweets_corpus_clean, random.order = F, max.words = 50, scale = c(3, 0.9), colors = rainbow(50, alpha = 0.8))

```

--- 

## making an analysis of negative Vs. positive words on the tweets:
now we used two text files, one containing positive words and the other contatining negative words.
we used those words to create an analysis on the twitts text and figured out the destribution of them on the twitts.

#####the numbers are between -3 to 3 while -3 is the most negative, 0 is neutral and 3 is the most positive

```{r POSNEG, echo=FALSE}

NBAtweets_text2 <- laply(NBAtweets, function(x) x$getText())

pos = scan('positive-words.txt', what = 'character', comment.char = ';')
neg = scan('negative-words.txt', what = 'character', comment.char = ';')

analysis = score.sentiment(NBAtweets_text2, pos.words = pos, neg.words = neg)

#table(analysis$score)
# an histogram of the destribution of negative/positive words from 500 NBA tweets
hist(analysis$score,xlab=" ", main="histogram of positive and negative words in NBA twitts ",
     border="black",col="skyblue")
# we can learn that there are more positive than negative tweets in this subject!

```

###from this graph we can learn that most of the twitts about NBA are neutrals. but we have more positive than negative content in this sport.

---

###now we'll see a graph which will tell us how many twitts from our 500 twitts are retwitted!

```{r, echo=FALSE }
# make a dataFrame from the tweets we got 
web_scraping_tweets <- twListToDF(NBAtweets)
barplot(table(web_scraping_tweets$isRetweet),col="green",main="retwitted twitts Vs. none")
```

### most of the times we will see more FALSE
### and its logical because usually only famous people twitts are retwitted.





#### the end